Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-06-06 paper/paper.tex
finish figure 5

\caption{\csentence{Six playing techniques of the violin.}
Subfigures:
(a) ordinario (with vibrato), (b) nonvibrato, (c) tremolo, (d) sforzando, (e) pizzicato (\emph{laissez vibrer}, i.e., let ring), and (f) staccato.
In each subfigure, the top image shows the wavelet scalogram, as a function of time $t$ (in seconds) and frequency $\lambda$ (in Hertz).
Conversely, the bottom image shows the average time--frequency scattering coefficients, as a function of temporal modulation rate $\alpha$ (in Hertz) and frequential modulation scale $\beta$ (in cycles per octave).
Darker shades denote greater values of acoustic energy.}
\label{fig:violin-scattering}
\end{figure}

>>>>

\caption{\csentence{Six playing techniques of the violin.}
Subfigures:
(a) ordinario (with vibrato), (b) nonvibrato, (c) tremolo, (d) sforzando, (e) pizzicato (\emph{laissez vibrer}, i.e., let ring), and (f) staccato.
In each subfigure, the top image shows the wavelet scalogram as a function of time $t$ (in seconds) and frequency $\lambda$ (in Hertz).
Conversely, the bottom image shows the average time--frequency scattering coefficients, as a function of temporal modulation rate $\alpha$ (in Hertz) and frequential modulation scale $\beta$ (in cycles per octave).
Darker shades denote greater values of acoustic energy.}
\label{fig:violin-scattering}
\end{figure}

\begin{figure}
\includegraphics[height=4cm]{figures/flute_scattering/Fl-ord-C4-mf_scalogram.pdf}
\hspace{8mm}
\includegraphics[trim=35 0 0 0, clip, height=4cm]{figures/flute_scattering/Fl-trill-maj2-C4-mf_scalogram.pdf}
\hspace{12mm}
\includegraphics[trim=35 0 0 0, clip, height=4cm]{figures/flute_scattering/Fl-ply+sng-Csharp4+C4-mf_scalogram.pdf}

\hspace{2mm}
\includegraphics[height=28mm]{figures/flute_scattering/Fl-ord-C4-mf_scattering.pdf}
\hspace{5mm}
\includegraphics[height=28mm]{figures/flute_scattering/Fl-trill-maj2-C4-mf_scattering.pdf}
\hspace{5mm}
\includegraphics[trim=0 0 77 0, clip, height=28mm]{figures/flute_scattering/Fl-ply+sng-Csharp4+C4-mf_scattering.pdf}

\hspace{12mm}
\csentence{(a) ordinario}\hspace{22mm}
\csentence{(b) trill $\mathsf{C_4} - \mathsf{D_4}$}\hspace{15mm}
\csentence{(c) play $\mathsf{C\musSharp_4}$ while singing $\mathsf{C_4}$}\vspace{1cm}

\includegraphics[height=4cm]{figures/flute_scattering/Fl-sfz-C4-fp_scalogram.pdf}
\hspace{8mm}
\includegraphics[trim=35 0 0 0, clip, height=4cm]{figures/flute_scattering/Fl-key-cl-C4-f_scalogram.pdf}
\hspace{12mm}
\includegraphics[trim=35 0 0 0, clip, height=4cm]{figures/flute_scattering/Fl-stacc-C4-mf_scalogram.pdf}

\hspace{2mm}
\includegraphics[height=28mm]{figures/flute_scattering/Fl-sfz-C4-fp_scattering.pdf}
\hspace{5mm}
\includegraphics[height=28mm]{figures/flute_scattering/Fl-key-cl-C4-f_scattering.pdf}
\hspace{5mm}
\includegraphics[trim=0 0 77 0, clip, height=28mm]{figures/flute_scattering/Fl-stacc-C4-mf_scattering.pdf}

\hspace{2mm}
\csentence{(d) sforzando}\hspace{25mm}
\csentence{(e) key click}\hspace{25mm}
\csentence{(f) staccato}\hspace{1mm}

\caption{\csentence{Six playing techniques of the flute.}
Subfigures:
(a) ordinario, (b) trill ($\mathsf{C_4} - \mathsf{D_4}$), (c) interference (play $\mathsf{C\musSharp_4}$ while singing $\mathsf{C_4}$), (d) sforzando, (e) key click, (f) staccato.
In each subfigure, the top image shows the wavelet scalogram as a function of time $t$ (in seconds) and frequency $\lambda$ (in Hertz).
Conversely, the bottom image shows the average time--frequency scattering coefficients, as a function of temporal modulation rate $\alpha$ (in Hertz) and frequential modulation scale $\beta$ (in cycles per octave).
Darker shades denote greater values of acoustic energy.}
\label{fig:flute}
\end{figure}
